Plots

### 2025-08-02 src/plots.Rmd
Bold max perf pccc plots

    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_point( # points
            color = "black",
            aes(
                shape = .data[[color]],
                fill = .data[[color]]
            ),
            size = mid_points_size
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, ": ", round(min_metric, 2))
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_start_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(
                    model_max, ": ", round(max_metric, 2),
                    " (R=", round(group_range, 2), ")"
                )
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            vjust = text_mid_vjust,
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_shape_manual(
            values = x_shapes,
            labels = x_color_labels,
            drop = ifelse(is.null(legend_add), T, F)
        ) +
        scale_fill_discrete(
            labels = x_color_labels,
            drop = ifelse(is.null(legend_add), T, F)
        ) +
        scale_x_continuous(
            limits = x_limits,
            breaks = x_breaks,
            expand = x_expand
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.position = legend_position,
            legend.title = legend_title,
            legend.margin = legend_margin,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )

>>>>

    # Plot metric for each model
    out <- ggplot(df_plot, aes(x = metric, y = .data[[group]])) +
        geom_segment( # min max lines
            data = df_ends,
            aes(
                x = min_metric,
                xend = max_metric,
                y = .data[[group]],
                yend = .data[[group]]
            ),
            linewidth = 0.75
        ) +
        geom_point( # points
            color = "black",
            aes(
                shape = .data[[color]],
                fill = .data[[color]]
            ),
            size = mid_points_size
        ) +
        geom_text( # min model text
            data = df_ends,
            aes(
                x = min_metric,
                y = .data[[group]],
                label = paste0(model_min, ": ", round(min_metric, 2))
            ),
            hjust = 1 + text_hjust,
            vjust = 0.5,
            size = text_start_size
        ) +
        geom_text( # max model text
            data = df_ends,
            aes(
                x = max_metric,
                y = .data[[group]],
                label = paste0(
                    model_max, ": ", round(max_metric, 2),
                    " (R=", round(group_range, 2), ")"
                )
            ),
            hjust = 0 - text_hjust,
            vjust = 0.5,
            size = text_end_size,
            fontface = "bold"
        ) +
        geom_text_repel( # mid model text
            data = df_mids,
            aes(label = model_label),
            color = "gray60",
            vjust = text_mid_vjust,
            max.overlaps = Inf,
            size = text_mid_size
        ) +
        scale_shape_manual(
            values = x_shapes,
            labels = x_color_labels,
            drop = ifelse(is.null(legend_add), T, F)
        ) +
        scale_fill_discrete(
            labels = x_color_labels,
            drop = ifelse(is.null(legend_add), T, F)
        ) +
        scale_x_continuous(
            limits = x_limits,
            breaks = x_breaks,
            expand = x_expand
        ) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.position = legend_position,
            legend.title = legend_title,
            legend.margin = legend_margin,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )
